Assessing the impacts of time to detection distribution assumptions on detection probability estimation

### 2017-03-04 Draft.tex
Last Adam updates to reviewer's comments and draft until: (i) simulations done, or (ii) Philip and Jarad review.
Discussion of the generalized gamma distribution.

We conducted three simulation studies to explore the behavior of models with non-constant TTDDs.
The first study compares mixture vs non-mixture models.
The second study compares the TTDD families.
In the first two studies, we utilized intercept only models to focus attention on robustness of the TTDD choice in the most simple of scenarios.
For the third study, we included fixed and random effects for both abundance and detection and again compared the distribution families. 
In all simulation studies, we focused on accuracy in estimation of $\pdet$ which then translated into estimation of abundance.

@@

>>>>

We conducted three simulation studies to explore the behavior of models with non-constant TTDDs.
The first study compares mixture vs non-mixture models.
The second study compares the TTDD families.
In the first two studies, we utilized intercept only models to focus attention on robustness of the TTDD choice in the most simple of scenarios.
For the third study, we included fixed and random effects for both abundance and detection and again compared the distribution families. 
Because our main goal with these studies was to demonstrate poor performance under model misspecification, and because the computation time for sampling from some models was large, we simulated only a small number of replicates.
In all simulation studies, we focused on accuracy in estimation of $\pdet$ which then translated into estimation of abundance.

@@

Just as the exponential TTDD is a special case of the two-parameter gamma and Weibull TTDDs, so all four TTDDs in our analysis are special cases the three-parameter generalized gamma distribution.
A generalized gamma TTDD encompasses a diversity hazard functions \citep{Cox2007}, eliminating the need to restrict analysis to lognormal, gamma, or Weibull TTDDs and the tail probabilities they imply.
However, maximum likelihood estimation of the generalized gamma has historically suffered from computational difficulties, unsatisifactory asymptotic normality at large sample sizes, and non-unique roots to the likelihood equation \citep{CoorayAnand2008, NoufailyJones2013}.
It may well be possible to implement our model with a generalized gamma TTDD, but especially when we consider the right-truncation of data from point-count surveys, we think model convergence would not be a trivial problem.

### 2017-03-04 ReviewerComments.tex
Discussion of the generalized gamma distribution.

Generalized Pareto: In another area in biology, in evolutionary genetics, the ``fitness" of individual variant strains has been modeled as coming from an exponential distribution.  For various reasons having to do with the biology of the system, such model was quickly challenged and pretty soon papers questioning the validity of this or this other model for data akin to your waiting times abounded. There is one pretty interesting paper by Beisel et al, 2007 (Genetics, 10.1534/genetics.106.068585), written towards the epiloge of such discussions, that posits that a particular parameterization of the Generalized Pareto distribution, with a single stroke, encompassed many suitable probabilistic models in the Weibull, Gumbel and Freched domain of attraction.  I wonder if the authors could write a general parameterization so that changing from one distribution to the other would simply amount to dialing a given parameter, much like Beisel et al do?  This would be just a practical
consideration that can at once deal with model selection and could speed up calculations
\begin{quote}
We appreciate the merit of the reviewer's suggestion and have added comments in the Discussion.
We focus our comments on a possible generalized gamma TTDD, which is an umbrella distribution that includes exponential, gamma, lognormal, and Weibull distributions as special cases.
The generalized Pareto analysis in \citet{Beisel2007} requires observations from the tail of the TTDD distribution, which we do not have.
Additionally, its focus is on flexible domains of attraction, whereas the TTDDs in our analysis are all from the Gumbel domain of attraction.
\adam{After researching the generalized gamma, add comments in the paragraph beginning `If the estimation of abundance is the primary interest...'.}
\end{quote}

@@

The authors could have crafted a beautiful and very telling graph (Figure 1) representing the multinomial intervals, the TTDD, the right censoring due to the end of the observation period, and the increased detection probability mixture component. Such figure (which is what I did by hand as I was reading the manuscript) would be a very useful guide in the reading of the paper.
\begin{quote}
We have added this as Figure \ref{M-fig:schematic}.
\adam{I have not citedthe figure in the text.  I am not convinced I need to.}
\end{quote}

>>>>

Generalized Pareto: In another area in biology, in evolutionary genetics, the ``fitness" of individual variant strains has been modeled as coming from an exponential distribution.  For various reasons having to do with the biology of the system, such model was quickly challenged and pretty soon papers questioning the validity of this or this other model for data akin to your waiting times abounded. There is one pretty interesting paper by Beisel et al, 2007 (Genetics, 10.1534/genetics.106.068585), written towards the epiloge of such discussions, that posits that a particular parameterization of the Generalized Pareto distribution, with a single stroke, encompassed many suitable probabilistic models in the Weibull, Gumbel and Freched domain of attraction.  I wonder if the authors could write a general parameterization so that changing from one distribution to the other would simply amount to dialing a given parameter, much like Beisel et al do?  This would be just a practical
consideration that can at once deal with model selection and could speed up calculations
\begin{quote}
We appreciate the merit of the reviewer's suggestion and have added comments in the Discussion.
We focus our comments on a possible generalized gamma TTDD, which is an umbrella distribution that includes exponential, gamma, lognormal, and Weibull distributions as special cases.
The generalized Pareto analysis in \citet{Beisel2007} requires observations from the tail of the TTDD distribution, which we do not have.
Additionally, its focus is on flexible domains of attraction, whereas the TTDDs in our analysis are all from the Gumbel domain of attraction.

Here are the comments we have added:
``Just as the exponential TTDD is a special case of the two-parameter gamma and Weibull TTDDs, so all four TTDDs in our analysis are special cases the three-parameter generalized gamma distribution.
A generalized gamma TTDD encompasses a diversity hazard functions \citep{Cox2007}, eliminating the need to restrict analysis to lognormal, gamma, or Weibull TTDDs and the tail probabilities they imply.
However, maximum likelihood estimation of the generalized gamma has historically suffered from computational difficulties, unsatisifactory asymptotic normality at large sample sizes, and non-unique roots to the likelihood equation \citep{CoorayAnand2008, NoufailyJones2013}.
It may well be possible to implement our model with a generalized gamma TTDD, but especially when we consider the right-truncation of data from point-count surveys, we think model convergence would not be a trivial problem."
\adam{This is an area of active research.  I feel like my tone is not optimistic enough.  Then again, it's not worth micro-wordsmithing.}
\end{quote}

@@

The authors could have crafted a beautiful and very telling graph (Figure 1) representing the multinomial intervals, the TTDD, the right censoring due to the end of the observation period, and the increased detection probability mixture component. Such figure (which is what I did by hand as I was reading the manuscript) would be a very useful guide in the reading of the paper.
\begin{quote}
We have added this as Figure \ref{M-fig:schematic}.
\adam{I have not cited the figure in the text.  I am not convinced I need to.}
\end{quote}
